Automated Topic Naming

### 2011-09-02 ese/ese.tex
updated figures for PG comparison

% numbers from mulan.tar.gz/maxdb.mulan.out.tex. I picked the two best learners for each db.
% The numbers are the micro and macro AUC numbers.
% MaxDB macro: BR NaN CLR NaN Homer NaN mlkNN Nan
% MaxDB micro: BR 0.77 CLR 0.67 Homer 0.61 mlkNN 0.67
% mysql macro: BR 0.74 CLR 0.65 mlKNN 0.61
% mysql micro: BR 0.81 CLR 0.8 mlkNN 0.78
% PgSQLn macro: BR 0.64 MlkNN 0.52
% PGSQLn micro: BR 0.65 MlkNN 0.59

\begin{figure*}[t]
\centering
\subfloat[MySQL]{
\includegraphics[width=0.3\textwidth]{figures/multi-label-results-mysql}
\label{fig:subfig3}
}
\subfloat[MaxDB]{
\includegraphics[width=0.3\textwidth]{figures/multi-label-results-maxdb}
\label{fig:subfig4}
}
\subfloat[PgSQL]{
\includegraphics[width=0.3\textwidth]{figures/multi-label-results-pgsql}
\label{fig:subfig5}
}
\caption[]{MySQL, PgSQL and MaxDB macro (grey) and micro (black) ROC results per multi-label learner. Possible values range from $0$--$1$.  Dashed line
indicates the performance of a random classifier.
%\todo[inline]{better discussion}% and graphical legend would be nice}
}
\label{fig:mulan}
\end{figure*}

@@

Figure~\ref{fig:mulan} presents the results of Mulan's best multi-label learners for our data. 
Calibrated Label Ranking (CLR) is a learner that builds two layers. The first layer determines if an entity should be labelled, while the second layer
determines what labels should be assigned.
The Hierarchy Of Multi-label classifiERs (HOMER) and Binary Relevance (BR) act as a hierarchy of learners: BR is flat, while HOMER tries to build a
deeper hierarchy for a more accurate learner~\cite{mulan}. 
These classifiers performed better than other multi-label classifiers as they have the best micro and macro ROC scores. 
The multi-label and single-label learners had similar performance: for
MySQL, BR and Naive Bayes had similar macro-ROC scores of $0.74$.
% although their results are comparable to the naive Bayesian learners we used in Section \ref{sec:suplabelling}.
% \todo[inline]{discuss this similarity in more detail}

>>>>

% Data source is src/validate/output/<db>.mulan.out.tex
% pgsqln & br & clr & homer
% macro-auc .64 .58 .58
% micro .65 .6 .6
%pgsqla
% macro .63 .56 .54
% micro .81 .81 .79
% maxdb (no macro)
% micro .77 .67 .61
% mysql
% macro .74 .65 .64
% micro .81 .8 .74

\begin{figure*}[t]
\centering
\subfloat[MySQL]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-mysql}
\label{fig:subfig3}
}
\subfloat[MaxDB]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-maxdb}
\label{fig:subfig4}
}
\caption[]{MySQL and MaxDB macro and micro-ROC results per multi-label learner. Possible values range from $0$--$1$.  Dashed line indicates the performance of a random classifier.
}
\label{fig:mulan}
\end{figure*}

\begin{figure}
\centering
\subfloat[Macro-ROC]{
\includegraphics[width=0.4\textwidth]{figures/pg-mulan-macro-compare}
\label{fig:pgcomp-a}
}
\subfloat[Micro-ROC]{
\includegraphics[width=0.4\textwidth]{figures/pg-mulan-micro-compare}
\label{fig:pgcomp-b}
}
\caption{Author \#1 and author \#2 ROC results for PostgreSQL.} 
\label{fig:pgcomp}
\end{figure}

@@

Figure~\ref{fig:mulan} presents the results of Mulan's best multi-label learners for our data. 
Calibrated Label Ranking (CLR) is a learner that builds two layers. The first layer determines if an entity should be labelled, while the second layer
determines what labels should be assigned.
The Hierarchy Of Multi-label classifiERs (HOMER) and Binary Relevance (BR) act as a hierarchy of learners: BR is flat, while HOMER tries to build a
deeper hierarchy for a more accurate learner~\cite{mulan}.

Figure~\ref{fig:pgcomp} shows the ROC results for the PostgreSQL product. In this figure, we show the relative differences when we use different training data sets. In \ref{fig:pgcomp-a} we see that ROC results are very similar. In the other figure, however, author \#1 has dramatically better performance. We speculate that this is due to the particular annotation decisions made by author \#1; in some sense he performed better. \todo{check this writeup of comparison. T-test useful}

These classifiers performed better than other multi-label classifiers as they have the best micro and macro ROC scores. 
The multi-label and single-label learners had similar performance: for
MySQL, BR and Naive Bayes had similar macro-ROC scores of $0.74$.
